\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage{charter}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is machine readable / ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ben Sodnomov} \\ \vspace{1pt}
    \small Toronto, ON $|$ 437-818-3190 $|$ \href{mailto:bsodnomovv@gmail.com}{\underline{bsodnomovv@gmail.com}} $|$
    \href{https://www.linkedin.com/in/buianto-sodnomov-9087672ba/}{\underline{linkedin.com/in/buianto}} $|$
    \href{https://github.com/reberie}{\underline{github.com/reberie}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    Software developer with internship experience shipping and supporting code across the full development lifecycle in \textbf{Agile} environments. Comfortable writing in multiple languages including \textbf{C\#}, \textbf{Java}, \textbf{Python}, and \textbf{JavaScript}, with hands-on experience building \textbf{RESTful APIs}, applying \textbf{authentication and authorization} patterns, and working with \textbf{CI/CD} pipelines. Published a cross-platform mobile app to the App Store. Takes ownership of work, communicates clearly across teams, and actively looks for ways to improve.
  }}
\end{itemize}
\vspace{-14pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: C\#, Java, Python, JavaScript, SQL, TypeScript} \\[1mm]
    \textbf{Frameworks \& Platforms}{: .NET, ASP.NET, Node.js, Express.js, React.js, React Native} \\[1mm]
    \textbf{APIs \& Security}{: RESTful APIs, SOAP-based Web Services, Authentication \& Authorization, OAuth, JWT, Secure API Handling, RBAC, OWASP} \\[1mm]
    \textbf{DevOps \& Version Control}{: Git, GitHub Actions, Jenkins, CI/CD Pipelines, TFS, Bitbucket, SonarQube, Unit Test Automation} \\[1mm]
    \textbf{Databases}{: SQL Server, PostgreSQL, MongoDB, Firebase} \\[1mm]
    \textbf{Cloud \& Tools}{: Azure, AWS, Jira, Confluence, GitHub Copilot, GenAI Tools, Postman} \\[1mm]
    \textbf{Practices}{: Agile Development, SDLC, Code Reviews, Debugging, Technical Documentation, Cross-platform Mobile Development}
  }}
\end{itemize}
\vspace{-14pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {\textbf{Computer Programming and Analysis (Advanced Diploma)}}{Jan 2024 -- Apr 2026}
    {Durham College}{Oshawa, ON}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Software Developer Intern}{May 2025 -- Aug 2025}
  {Giesecke+Devrient}{Markham, ON}
  \resumeItemListStart
    \resumeItem{Worked across the full \textbf{software development lifecycle} in an \textbf{Agile} environment alongside developers, QA, and business stakeholders.}
    \resumeItem{Troubleshot and resolved defects in \textbf{.NET} and \textbf{ASP.NET}-based workflows, ran test cases, and supported incident analysis to improve application stability.}
    \resumeItem{Used \textbf{SonarQube} to support code quality checks and unit test coverage, reaching at least \textbf{50\% code coverage} across targeted modules.}
    \resumeItem{Contributed to build and deployment processes using \textbf{Jenkins}, \textbf{Nexus}, and \textbf{CI/CD} pipelines.}
    \resumeItem{Helped migrate version control from \textbf{TFS to Bitbucket}, improving code review workflows and team collaboration.}
    \resumeItem{Wrote and maintained over \textbf{50+ pages of technical documentation in Confluence} to support team reference and knowledge transfer.}
  \resumeItemListEnd

\resumeSubheading
  {Peer Coach}{Oct 2025 -- Present}
  {Durham College}{Oshawa, ON}
  \resumeItemListStart
    \resumeItem{Provided one-on-one coaching to help students break down goals, stay organized, and follow through on plans.}
    \resumeItem{Adapted communication style to individual needs, working styles, and levels of prior knowledge.}
    \resumeItem{Built trust with students facing academic challenges by listening carefully and guiding problem-solving without taking over.}
  \resumeItemListEnd

\resumeSubheading
  {A/V Technician}{Sep 2024 -- Apr 2025}
  {Durham College}{Oshawa, ON}
  \resumeItemListStart
    \resumeItem{Diagnosed and resolved technical issues during live events with limited time and support.}
    \resumeItem{Managed and tracked \textbf{1000+} pieces of equipment using Microsoft Excel.}
    \resumeItem{Took initiative to ensure setups ran smoothly, including work outside standard hours when needed.}
  \resumeItemListEnd

\resumeSubheading
  {Peer Tutor}{May 2024 -- Apr 2025}
  {Durham College}{Oshawa, ON}
  \resumeItemListStart
    \resumeItem{Provided one-on-one academic support to \textbf{3+} students per week, explaining technical concepts and guiding problem-solving.}
    \resumeItem{Gave feedback on \textbf{5+} assignments per week, helping students improve understanding and quality of work.}
    \resumeItem{Built experience explaining technical material clearly to people with different levels of familiarity.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
  {\textbf{PuffZero -- Mobile App}}{Feb 2024 -- Aug 2024}
  {Personal Project}{}
  \resumeItemListStart
    \resumeItem{\textbf{App Store:} \href{https://apps.apple.com/ca/app/puff-zero-quit-vaping-tracker/id6746369660}{\underline{puff-zero-quit-vaping-tracker}}}
    \resumeItem{Designed and developed a cross-platform mobile application using \textbf{React Native} and \textbf{Expo}.}
    \resumeItem{Worked with a designer to build and revise the user interface based on product needs and technical limits.}
    \resumeItem{Gained experience with application design, API integration, debugging, testing, and deployment.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}